---
title       : 大数据时代，再造创造力
subtitle    : 创造力研究及机器学习展示
author      : 朱浚铭 Jeremy
job         : 商业分析在读博士
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : [bootstrap, quiz, shiny, interactive]
ext_widgets : {rCharts: [libraries/nvd3, libraries/highcharts]}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides

---

## 简介

1. Edit YAML front matter
2. Write using R Markdown
3. Use an empty line followed by three dashes to separate slides!

--- .class #id 

## Slide 2

1. Paste
2. Copy

---
## 放大创造力

- map your circles of creativity, let creative people share ideas with each other. Someday, they will surprise you. 
- you also need to identify your creativity brokers -- people with good judgement and access to resources. 
- it’s also important to move toward multi-generational leadership teams.
- You should also be ready to change your consumer frame. 
- be a platform for creativity. 
By Bruce Nussbaum

--- &radio
## Question 1

What is 1 + 1?

1. 1
2. _2_
3. 3
4. 4

*** .hint
This is a hint

*** .explanation
This is an explanation## Question 1

---

## Interactive Chart

```{r echo = F, results = 'asis'}
require(rCharts)
haireye = as.data.frame(HairEyeColor)
n1 <- nPlot(Freq ~ Hair, group = 'Eye', type = 'multiBarChart',
  data = subset(haireye, Sex == 'Male')
)
n1$print('chart1')
```

--- &interactive

## Interactive Console

```{r opts.label = 'interactive', results = 'asis'}
require(googleVis)
M1 <- gvisMotionChart(Fruits, idvar = 'Fruit', timevar = 'Year')
```

```{r results='asis'}
print(M1, 'chart')
```

---

## Interactive Chart with Shiny Controls

```{r echo = F, opts.label = 'shiny'}
slidifyUI(
  sidebarPanel(
    selectInput('sex', 'Choose Sex', c('Male', 'Female')),
    selectInput('type', 'Choose Type',
      c('multiBarChart', 'multiBarHorizontalChart')
    )
  ),
  mainPanel(
    tags$div(id = 'nvd3plot', class='shiny-html-output nvd3 rChart')
  )
)
```

--- &interactive

## Interactive Console

```{r opts.label = 'interactive', results = 'asis'}
require(rCharts)
a <- Highcharts$new()
a$chart(type = "spline")
a$series(data = c(1, 3, 2, 4, 5, 4, 6, 2, 3, 5, NA), dashStyle = "longdash")
a$series(data = c(NA, 4, 1, 3, 4, 2, 9, 1, 2, 3, 4), dashStyle = "shortdot")
a$legend(symbolWidth = 80)
a$print('chart3')
```

--- &interactive

## Results = Markup

```{r opts.label = 'interactive', results = 'markup'}
require(xtable)
options(xtable.type = 'html')
xtable(head(mtcars))
```

--- &interactive

## Interactive economic 

```{r opts.label = 'interactive', results='markup'}
data(economics, package = "ggplot2")
econ = transform(economics, date = as.character(date))
m1 = mPlot(x = "date", y = c("psavert", "uempmed"), type = "Line", data = econ)
m1$set(pointSize = 0, lineWidth = 1)
m1
```

